FoRTE baseline

### 2019-04-22 analysis/paper/paper.Rmd
Minor cleanup of methods outline

- **Introduction**
- **Methods**
    - Site description
    - ED2 model description
        - Common features
        - Submodel descriptions (in brief; more details in appendices)
            - Two-stream RTM
            - Multiple-scatter RTM
            - Finite canopy radius model
            - Trait plasticity scheme
            - N limitation (?)
    - Data sources
        - TRY data
        - Other data? FIA? Remote sensing?
    - Modeling workflow (PEcAn, etc.)
    - Data analysis
        - Structural vs. parametric uncertainty
        - Comparison against "reality"
- **Results**
    - Summary:
        - LAI time series with uncertainties, faceted by model structure
    - Structural uncertainty details
        - Understory light environment and how it affects species matters
        - The multiple-scatter
            - Fig: RTM comparison (Radiation profile)
            - Fig: Crown model comparison
            - Fig: Trait plasticity?
    - Uncertainty analysis
        - Which parameters contribute the most uncertainty?
        - Structural vs. parameteric uncertainty
- **Discussion**
    - Ecological implications of structural uncertainty
        - Predictions about ecological succession are very sensitive to the understory light environment.
            - Need a good representation of canopy structure (finite canopy radius)
            - How you model canopy radiative transfer matters! Small differences in the model can give significant results.
        - But, trait plasticity can provide an alternative mechanism for success in the understory.
            - Important modeling implication for all the emerging research on intra-specific trait variability.
            - This combination of discrete functional types with plastic traits is closer to reality than purely trait-based ("eco-evolutionary?") models or completely discretized models with static traits on the other.
            - Important caveat: Current implementation is based entirely on tropical data, which has more extreme canopy shading than temperate forests (REF), so tropical species may have evolved stronger trait plasticity than temperate species (REF).
    - Implications of uncertainty analysis for future data collection and model development
        - Parameter uncertainty is still a _huge_ source of overall model predictive uncertainty. Different parameters can give _qualitatively_ different ecological outcomes.
        - Looking beyond aggregate variables (e.g. net primary productivity, total LAI) is essential to model evaluation and calibration. It's possible to generate a relatively?
        - (Expected) Subsurface parameters (e.g. leaf-root ratios) have high sensitivity, but are poorly constrained.
        - Trait covariance may alleviate some data limitation (Shiklomanov et al. 2018 [preprint])
    - Future directions: Predicting disturbance response
        - FoRTE project -- Forecasting a disturbance.
            - Compare ecological resilience/memory between model and reality

@@

## Model description: ED2

The Ecosystem Demography Model, version 2.2 (ED2).
Default configuration is described in [@longo_2019_ed1].
A brief summary of common features is as follows:

- Cohort-based scaling approach
- Photosynthesis / stomatal conductance
    - I think I need to cite @katul_2003_relationship somewhere in here
- Allometries

@@

@@

Other data from FoRTE? FIA? Remote sensing?

@@

{TODO: Conceptual diagram of workflow}

@@

Photosynthesis / respiration ratio (i.e. C balance) in light and shade can be used as an indication of succession -- expect early successional species to have higher ratio in light and late successional species to have higher ratio in shade [@bazzaz_1979_physiological].

>>>>

- **Results**
    - Summary:
        - LAI time series with uncertainties, faceted by model structure
    - Structural uncertainty details
        - Understory light environment and how it affects species matters
        - The multiple-scatter
            - Fig: RTM comparison (Radiation profile)
            - Fig: Crown model comparison
            - Fig: Trait plasticity?
    - Uncertainty analysis
        - Which parameters contribute the most uncertainty?
        - Structural vs. parameteric uncertainty
- **Discussion**
    - Ecological implications of structural uncertainty
        - Predictions about ecological succession are very sensitive to the understory light environment.
            - Need a good representation of canopy structure (finite canopy radius)
            - How you model canopy radiative transfer matters! Small differences in the model can give significant results.
        - But, trait plasticity can provide an alternative mechanism for success in the understory.
            - Important modeling implication for all the emerging research on intra-specific trait variability.
            - This combination of discrete functional types with plastic traits is closer to reality than purely trait-based ("eco-evolutionary?") models or completely discretized models with static traits on the other.
            - Important caveat: Current implementation is based entirely on tropical data, which has more extreme canopy shading than temperate forests (REF), so tropical species may have evolved stronger trait plasticity than temperate species (REF).
    - Implications of uncertainty analysis for future data collection and model development
        - Parameter uncertainty is still a _huge_ source of overall model predictive uncertainty. Different parameters can give _qualitatively_ different ecological outcomes.
        - Looking beyond aggregate variables (e.g. net primary productivity, total LAI) is essential to model evaluation and calibration. It's possible to generate a relatively?
        - (Expected) Subsurface parameters (e.g. leaf-root ratios) have high sensitivity, but are poorly constrained.
        - Trait covariance may alleviate some data limitation (Shiklomanov et al. 2018 [preprint])
    - Future directions: Predicting disturbance response
        - FoRTE project -- Forecasting a disturbance.
            - Compare ecological resilience/memory between model and reality

@@

## ED2 model description

The Ecosystem Demography Model, version 2.2 (ED2).
Default configuration is described in [@longo_2019_ed1].

@@

BETYdb [@lebauer_2013_facilitating].

@@

Other FoRTE data?

@@

For each combination of ED submodels, we ran 10 ED ensemble simulations.

@@

- Structural vs. parameteric uncertainty
- Comparison against observations
- Others...
